Equations & R Code

### 2017-02-21 manuscript/coexistence-stability_ms.Rmd
lots of updates for figure 2 in manuscript; updates code to correct version and achieves relative nonlinearity curve

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \doublespacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={footnotesize},labelfont={sf,bf},labelsep=space]{caption}
  - \usepackage{sectsty}
  - \usepackage{bm,mathrsfs}
  - \usepackage{mathptmx} 
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology_letters.csl

@@

\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\definecolor{blue}{rgb}{0,0,0.7} 
\newcommand{\new}{\textcolor{blue}}
<!--
\allsectionsfont{\normalfont\sffamily\bfseries}
-->

@@

\noindent \textbf{Number of Words}: 3,699

\noindent \textbf{Number of References}: 40

@@

ACKNOWLEDGMENTS
---------------
The National Science Foundation provided funding for this work through a Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a CAREER award to PBA (DEB-1054040). We thank four anonymous reviewers for providing detailed and thoughtful comments that greatly improved the paper.

@@

\begin{table}[!htbp]
\footnotesize
\caption{Default values of model parameters and their descriptions. Parameters that vary depending on the mode and strength of species coexistence or depending on species competitive hierarchies are labeled as ``variable'' in parentheses. The dormant-to-live biomass transition fraction ($\gamma$) is a function of other parameters, so has no default value.}
\begin{tabular}{l l l}
\hline
Parameter & Description & Value \\
\hline
$r$ & maximum per capita growth rate & 0.2 (variable) \\
$a$ & Hill function rate parameter & 2 (variable) \\
$b$ & Hill function curvature parameter & 2.5 (variable) \\
$\epsilon$ & resource-to-biomass conversion efficiency & 0.5 \\
$\alpha$ & allocation fraction of live biomass to dormant biomass & 0.5 (variable) \\
$\gamma$ & dormant-to-live biomass transition fraction & -- \\
$\rho$ & correlation of species' response to the environment & 0 (variable) \\
$\sigma_E$ & variance of the environmental cue & 2 (variable) \\
$\eta$ & dormant biomass mortality rate & 0.1 \\
$\mu(R^+)$ & mean annual resource pulse & 20 \\
$\sigma(R^+)$ & standard deviation of annual resource pulse & 0 (variable) \\
\hline
\end{tabular}
\end{table}

@@

# mytheme <- theme_bw()+
#   theme(panel.grid.major.x = element_blank(), 
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         panel.grid.major.y = element_blank(),
#         panel.background   = element_rect(fill = "white"),
#         axis.text          = element_text(size=6, color="grey35", family = "Arial Narrow"),
#         axis.title         = element_text(size=8, family = "Arial Narrow", face = "bold"),
#         panel.border       = element_blank(),
#         axis.line.x        = element_line(color="black"),
#         axis.line.y        = element_line(color="black"),
#         strip.background   = element_blank(),
#         strip.text         = element_text(size=8, color="grey35", family = "Arial Narrow"),
#         legend.title       = element_text(size=8, family = "Arial Narrow"),
#         legend.text        = element_text(size=6, color="grey35", family = "Arial Narrow"),
#         legend.key.size    = unit(0.3, "cm"))

@@

# mycols <- c("#9D6188","#97A861")
# mycols <- c("black", "red")
# mycols <- c("grey35", "steelblue")
# mycols <- viridis(2, end = 0.6)
mycols <- brewer.pal(3, "Set2")

# mytheme <- theme(axis.text=element_text(size=6),
#                  axis.title=element_text(size=8),
#                  legend.text=element_text(size=6),
#                  legend.key.size=unit(0.3, "cm"))

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure1.png}
  \caption{Variability of total community biomass as a function of species richness when coexistence is maintained by the storage effect (A,B) or relative nonlinearity (C,D). Left panels show results from simulations where environmental or resource variance determine the number species that coexist in a community. Right panels show results from simulations where environmental or resource variance is fixed at a level that allows coexistence of all four species, but species are removed to manipulate diversity. The left-hand panels represent regional diversity-variability relationships across natural diversity gradients, whereas the right-hand panels represent local diversity-variability relationships. Parameter values, where species are denoted by numeric subscripts: (A) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 0$, $\sigma_E =$ variable; (B) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = -1/3$, $\sigma_E = 4$; (C) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ variable; (D) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ 1.2.}
\end{figure}

>>>>

---
layout: 12pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \usepackage{todonotes}
  - \doublespacing
  - \usepackage{rotating}
  - \usepackage{color, soul}
  - \usepackage[font={normalsize},labelfont={bf},labelsep=quad]{caption}
  - \usepackage{sectsty}
  - \usepackage{bm,mathrsfs}
  - \usepackage{mathptmx} 
bibliography: ~/Dropbox/Bibliography/CoexistStability.bib
csl: components/ecology_letters.csl

@@

\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{gray}}
\definecolor{blue}{rgb}{0,0,0.7} 
\newcommand{\new}{\textcolor{blue}}

@@

\noindent \textbf{Number of Words in Abstract}: \textcolor{red}{UPDATE}

\noindent \textbf{Number of Words in Main Text}: \textcolor{red}{UPDATE}

\noindent \textbf{Number of References}: \textcolor{red}{UPDATE}

@@

ACKNOWLEDGMENTS
---------------
The National Science Foundation provided funding for this work through a Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a CAREER award to PBA (DEB-1054040). \new{We thank four anonymous reviewers for providing detailed and thoughtful comments that greatly improved the paper.}

@@

\begin{table}[!htbp]
\caption{Default values of model parameters and their descriptions. Parameters that vary depending on the mode and strength of species coexistence or depending on species competitive hierarchies are labeled as ``variable'' in parentheses. The dormant-to-live biomass transition fraction ($\gamma$) is a function of other parameters, so has no default value.}
\begin{tabular}{l l l}
\hline
Parameter & Description & Value \\
\hline
$r$ & maximum per capita growth rate & 0.2 (variable) \\
$a$ & Hill function rate parameter & 2 (variable) \\
$b$ & Hill function curvature parameter & 2.5 (variable) \\
$\epsilon$ & resource-to-biomass conversion efficiency & 0.5 \\
$\alpha$ & allocation fraction of live biomass to dormant biomass & 0.5 (variable) \\
$\gamma$ & dormant-to-live biomass transition fraction & n.a. \\
$\rho$ & correlation of species' response to the environment & 0 (variable) \\
$\sigma_E$ & variance of the environmental cue & 2 (variable) \\
$\eta$ & dormant biomass mortality rate & 0.1 \\
$\mu(R^+)$ & mean annual resource pulse & 20 \\
$\sigma(R^+)$ & standard deviation of annual resource pulse & 0 (variable) \\
\hline
\end{tabular}
\end{table}

@@

set.seed(12345)

@@

mycols <- brewer.pal(3, "Set2")

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=5in]{/Users/atredenn/Google_Drive/coexistence-stability_submission/figures/coex_stability_figure1.png}
  \caption{Variability of total community biomass as a function of species richness when coexistence is maintained by the storage effect (A,B) or relative nonlinearity (C,D). Left panels show results from simulations where environmental or resource variance determine the number species that coexist in a community. Right panels show results from simulations where environmental or resource variance is fixed at a level that allows coexistence of all four species, but species are removed to manipulate diversity. The left-hand panels represent regional diversity-variability relationships across natural diversity gradients, whereas the right-hand panels represent local diversity-variability relationships. Points are jittered within discrete richness values for visual clarity. Parameter values, where species are denoted by numeric subscripts: (A) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 0$, $\sigma_E =$ variable; (B) $r_1 = r_2 = r_3 = r_4 = 0.2$, $a_1 = a_2 = a_3 = a_4 = 2$, $b_1 = b_2 = b_3 = b_4 = 2.5$, $\alpha_1 = 0.5, \alpha_2 = 0.49, \alpha_3 = 0.48, \alpha_4 = 0.47$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = -1/3$, $\sigma_E = 4$; (C) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ variable; (D) $r_1 = 0.2, r_2 = 1, r_3 = 2, r_4 = 5$, $a_1 = 2, a_2 = 5, a_3 = 10, a_4 = 25$, $b_1 = 2.5, b_2 = 20, b_3 = 30, b_4 = 45$, $\alpha_1 = \alpha_2 = \alpha_3 = \alpha_4 = 0.5$, $\rho_1 = \rho_2 = \rho_3 = \rho_4 = 1$, $\sigma(R^+) =$ 1.1.}
\end{figure}

### 2017-02-21 manuscript/coexistence-stability_ms.tex
lots of updates for figure 2 in manuscript; updates code to correct version and achieves relative nonlinearity curve

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{rotating}
\usepackage{color, soul}
\usepackage[font={footnotesize},labelfont={sf,bf},labelsep=space]{caption}
\usepackage{sectsty}
\usepackage{bm,mathrsfs}
\usepackage{mathptmx}

@@

The National Science Foundation provided funding for this work through a
Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a
CAREER award to PBA (DEB-1054040). We thank four anonymous reviewers for
providing detailed and thoughtful comments that greatly improved the
paper.

>>>>

\usepackage{lineno}
\linenumbers
\usepackage{setspace}
\usepackage{todonotes}
\doublespacing
\usepackage{rotating}
\usepackage{color, soul}
\usepackage[font={normalsize},labelfont={bf},labelsep=quad]{caption}
\usepackage{sectsty}
\usepackage{bm,mathrsfs}
\usepackage{mathptmx}

@@

The National Science Foundation provided funding for this work through a
Postdoctoral Research Fellowship in Biology to ATT (DBI-1400370) and a
CAREER award to PBA (DEB-1054040).
\new{We thank four anonymous reviewers for providing detailed and thoughtful comments that greatly improved the paper.}
